Discrimination in police award nomination in Chicago

### 2024-02-14 outputs/paper/paper.qmd
Updated Tables/Models

```{r}
#| label: Figure 1 ()
#| fig-cap: Bills of penguins
#| echo: false
ggplot(all_officer, aes(x=total_month, y=arrest)) + 
  geom_point(shape=18, color="blue")

ggplot(all_officer, aes(x=arrest - Complaints, y=awd_perf)) + 
  geom_point(shape=18, color="blue")

>>>>

```{r}
#| label: Figure 1 ()
#| fig-cap: Bills of penguins
#| echo: false

ggplot(all_officer, aes(x = Complaints, y = awd_perf)) + 
  geom_point(shape=18, color="blue")

ggplot(all_officer, aes(x = arrest, y = awd_perf)) + 
  geom_point(shape=18, color="blue")
```
